Model-View-Controller Package

### 2006-04-26 inst/doc/MVCClass.Rnw
Added a new method: identifyView.
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MVCClass@17721 bc3139a8-67e5-0310-9ffc-ced21a209358

Several generic functions have been defined that refer to operations 
performed on views.  These generic functions are \Rfunction{motionEvent}, 
\Rfunction{clickEvent}, \Rfunction{updateView}, and \Rfunction{redrawView}.  
Methods for these generic 
functions will be defined in packages that use this package (in 
\Rpackage{iSPlot} and \Rpackage{iSNetwork}).  When these methods are defined, 
the \Rfunction{motionEvent} method will be used to respond to a mouse over 
event on a view, the \Rfunction{clickEvent} method will be used to respond to 
a click event over a view, the \Rfunction{updateView} method will be used to 
update only a portion of the view, and the \Rfunction{redrawView} method will 
be used to completely redraw the view.

>>>>

Several generic functions have been defined that refer to operations 
performed on views.  These generic functions are \Rfunction{motionEvent}, 
\Rfunction{clickEvent}, \Rfunction{updateView}, \Rfunction{redrawView} and
\Rfunction{identifyView}.  Methods for these generic 
functions will be defined in packages that use this package (in 
\Rpackage{iSPlot} and \Rpackage{iSNetwork}).  When these methods are defined, 
the \Rfunction{motionEvent} method will be used to respond to a mouse over 
event on a view, the \Rfunction{clickEvent} method will be used to respond to 
a click event over a view, the \Rfunction{updateView} method will be used to 
update only a portion of the view, the \Rfunction{redrawView} method will 
be used to completely redraw the view, and the \Rfunction{identifyView} method
will be used to identify an object (such as a point, a node, etc.) on a view.
